Similarity of public submissions to Austria's amendment of the epidemic law

### 2021-01-06 _posts/2020-12-22-submissionsepidemiclaw/submissionsepidemiclaw.Rmd
post submission: removed files from subfolder => now all _blog_data

```{r include=FALSE}
df_submission <- readr::read_csv2(file="submissionsepidemiclaw_files/df_submission_rss.csv")

@@

```{r include=FALSE}
# load saved links to pdf_files
df_submission <- readr::read_csv2(file="submissionsepidemiclaw_files/df_submission.csv")

@@

```{r echo=FALSE}
df_sozial_sim <- readr::read_csv2(file="submissionsepidemiclaw_files/df_bar_sim_sozial.csv") %>% 
  mutate(law="Sozialhilfegrundgesetz")

>>>>

```{r include=FALSE}
# df_submission <- readr::read_csv2(file="submissionsepidemiclaw_files/df_submission_rss.csv")
df_submission <- readr::read_csv2(file=here::here("_blog_data",                              "epidemic_law_submissions", "df_submission_rss.csv"))

@@

```{r include=FALSE}
# load saved links to pdf_files
# df_submission <- readr::read_csv2(file="submissionsepidemiclaw_files/df_submission.csv")
df_submission <- readr::read_csv2(file=here::here("_blog_data", "epidemic_law_submissions","df_submission.csv"))

@@

```{r echo=FALSE}
df_sozial_sim <- readr::read_csv2(file=here::here("_blog_data", "epidemic_law_submissions", "df_bar_sim_sozial.csv")) %>%  mutate(law="Sozialhilfegrundgesetz")
